Label object representation and manipulation with ITK

### 2007-09-20 article/Article.tex
add the PhysicalSizeOnBorder attribute
darcs-hash:20070920143450-2fc9d-494b4be0990dbbb4c8e7a181769629bd3dc5c4a4.gz

The {\em itk::LabelObject} class represent the label obejcts. It has two main
features:
\begin{itemize}
  \item It manage the set pixels which compose the object. The pixels are stored
using the run-length encoding.
  \item It has a label.
\end{itemize}

@@

\begin{itemize}
  \item {\em Size} is the size of the object in number of pixels. Its type is
{\em unsigned long}.
  \item {\em PhysicalSize} is the size of the object in physical unit. It is equal
to the {\em Size} multiplicated by the physical pixel size. Its type is {\em double}.
  \item {\em Centroid} is the position of the center of the shape in physical coordinates. It is not
constrained to be in the object, and thus can be outside if the object is not convex.
Its type is {\em Point< double, ImageDimension >}. 
  \item {\em Region} is the bounding box of the object given in the pixel coordinates.
The physical coordinate can easily be computed from it. Its type is
{\em ImageRegion< ImageDimension >}.
  \item {\em RegionElongation} is the ratio of the longest physical size of the region
on one dimension and its smallest physical size. This descriptor is not robust, and in
particular is sensitive to rotation. Its type is {\em double}.
  \item {\em SizeRegionRatio} is the ratio of the size of the object region (the
bounding box) and the real size of the object. Its type is {\em double}.
  \item {\em SizeOnBorder} is the number of pixels in the objects which are on the border
of the image. This attribute is particulary useful to remove the objects which are touching
too much the border. Its type is {\em unsigned long}.
  \item {\em FeretDiameter} is the diameter in physical units of the sphere which include
all the object. The feret diameter is not computed by default, because of its high computation.
Its type is {\em double}.
  \item {\em BinaryPrincipalMoments} contains the principal moments. Its type is
{\em itk::Vector< double, ImageDimension >}.
  \item {\em BinaryPrincipalAxes} contains the principal axes of the object. Its type is
{\em itk::Matrix< double, ImageDimension, ImageDimension >}.
  \item {\em BinaryElongation} is the elongation of the shape, computed as the ratio
of the largest principal moment by the smallest principal moment. Its value is greater
or equal to $1$· Its type si {\em double}.
%   \item {\em Perimeter}
\end{itemize}

>>>>

The {\em itk::LabelObject} class represent the label objects. It has two main
features:
\begin{itemize}
  \item It manage the set pixels which compose the object. The pixels are stored
using the run-length encoding.
  \item It has a label.
\end{itemize}

@@

\begin{itemize}
  \item {\em Size} is the size of the object in number of pixels. Its type is
{\em unsigned long}.
  \item {\em PhysicalSize} is the size of the object in physical unit. It is equal
to the {\em Size} multiplicated by the physical pixel size. Its type is {\em double}.
  \item {\em Centroid} is the position of the center of the shape in physical coordinates. It is not
constrained to be in the object, and thus can be outside if the object is not convex.
Its type is {\em Point< double, ImageDimension >}. 
  \item {\em Region} is the bounding box of the object given in the pixel coordinates.
The physical coordinate can easily be computed from it. Its type is
{\em ImageRegion< ImageDimension >}.
  \item {\em RegionElongation} is the ratio of the longest physical size of the region
on one dimension and its smallest physical size. This descriptor is not robust, and in
particular is sensitive to rotation. Its type is {\em double}.
  \item {\em SizeRegionRatio} is the ratio of the size of the object region (the
bounding box) and the real size of the object. Its type is {\em double}.
  \item {\em SizeOnBorder} is the number of pixels in the objects which are on the border
of the image. A pixel on several borders (a pixel in a corner) is counted only one time, so the
size on border can't be greater than the size of the object.
This attribute is particulary useful to remove the objects which are touching
too much the border. Its type is {\em unsigned long}.
  \item {\em PhysicalSizeOnBorder} is the physical size of the objects which are on the border
of the image. In 2D, it is a distance, in 3D, a surface, etc. Contrary to the {\em PhysicalSize}
attribute which is directly linked to the {\em Size}, this attribute is not directly
linked to the {\em SizeOnBorder} attribute. This attribute is particulary useful to remove
the objects which are touching too much the border. Its type is {\em double}.
  \item {\em FeretDiameter} is the diameter in physical units of the sphere which include
all the object. The feret diameter is not computed by default, because of its high computation.
Its type is {\em double}.
  \item {\em BinaryPrincipalMoments} contains the principal moments. Its type is
{\em itk::Vector< double, ImageDimension >}.
  \item {\em BinaryPrincipalAxes} contains the principal axes of the object. Its type is
{\em itk::Matrix< double, ImageDimension, ImageDimension >}.
  \item {\em BinaryElongation} is the elongation of the shape, computed as the ratio
of the largest principal moment by the smallest principal moment. Its value is greater
or equal to $1$· Its type si {\em double}.
%   \item {\em Perimeter}
\end{itemize}
